Manuscript plots

### 2025-02-11 manuscript_modelling_and_plots.Rmd
adding notes on exactly what some of functions do
updates

*add_epred_draws()* adds draws from the expectation of the posterior predictive distribution. Provides the expected means from the model. The default for the re_formula is NULL which includes the groups level effects which thus produces marginal effects (incorportates the random effects in the estimate).

@@

@@

summary(gte.fit.6)[["fixed"]][3,1] + 1.96 * ran.effects
summary(gte.fit.6)[["fixed"]][3,1] - 1.96 * ran.effects
```

>>>>

*add_epred_draws()* adds draws from the expectation of the posterior predictive distribution. Provides the expected means from the model. The default for the re_formula is NULL which includes the groups level effects which thus produces marginal effects (incorportates the random effects in the estimate). When this is plotted along with intervals, it refers to the posterior mean alongside 50% and 95% quantile credible intervals.

@@

# loading gte model
gte.fit.6 <- readRDS(here::here("gaze_entropy_heterogenous/models/gte_fit_6.rds"))

@@

summary(gte.fit.6)[["fixed"]][3,1] + 1.96 * ran.effects
summary(gte.fit.6)[["fixed"]][3,1] - 1.96 * ran.effects

#
ppid.effects <- cbind(ppid = rownames(ppid.effects), ppid.effects)

ppid.effects <- merge(ppid.effects, participant.info, by = c("ppid"))

ggplot(ppid.effects, mapping = aes(age, ranef)) +
  geom_point() +
  geom_smooth(method = "lm")

```
